---
title: "HW2"
author: ""
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rstanarm)
```

# HW2

### Q1. (4 points)

With binary regression, "separation" is a common problem. This occurs when a continuous predictor is perfectly separated with all zeros below a certain point and all zeros above a certain point. See the simulated data below for an example.

```{r}
x <- seq(-1, 1, length.out = 20)
y <- rep(c(0,1), each = 10)

df_sep <- tibble(x=x, y=y)

df_sep %>% ggplot(aes(y=y, x=x)) + geom_point() + theme_bw()
```

Using both `glm` and `stan_glm` with a probit link to fit the data. Identify the differences in the model output and discuss why they might differ.

### Q2. (4 points)

Revisiting STAT505 HW 9, Q3.

```{r}
candy <- read_csv("https://math.montana.edu/ahoegh/teaching/stat446/candy-data.csv")
```

Use the candy dataset and a probit regression model to analyze the relationship between one or two predictors in the dataset and the outcome (whether the candy contains chocolate). Describe how each input affects Pr[chocolate = 1].

### Q3. (6 points)

Using a dataset with Yelp scores in Madison, Wisconsin, model the probability of 1-star, 2-star, 3-star, 4-star, and 5-star reviews as a function of the two included neighborhoods. Summarize the model parameters and make a graphic / table (preferably a graphic) to display your results.

```{r}
set.seed(01312021)
yelp_biz <- read_csv("https://math.montana.edu/ahoegh/teaching/stat532/data/yelp_biz_info.csv") %>% 
  filter(neighborhood %in% c("South Campus",'Williamson - Marquette'))
yelp_reviews <- read_csv("https://math.montana.edu/ahoegh/teaching/stat532/data/yelp_biz_reviews.csv")

yelp_comb <- yelp_reviews %>% 
  right_join(yelp_biz, by = 'business_id') %>% 
  mutate(stars = factor(stars)) 
```

